---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ConjointSensitivity

<!-- badges: start -->
<!-- badges: end -->

This package is developed to evaluate the robustness of conjoint analysis results to the removal of small fractions of respondents and experimentally generated unique contests.

Our package is built on ```zaminfluence``` to calculate influence scores and detect the most influential respondents and contests in conjoint designs. 

We provide a simple example to demonstrate how to use ```ConjointSensitivity``` using the replication data for the non-partisan YouGov experiment in Kirkland and Coppock (2018).

## References
*   **zaminfluence Package & Methodology:** Broderick, T., Giordano, R., & Meager, R. (2020). _An Automatic Finite-Sample Robustness Metric: When Can Dropping a Little Data Make a Big Difference?_

*   **Kirkland and Coppock (2018) Data:** Kirkland, P. A., & Coppock, A. (2018). _Candidate choice without party labels: new insights from conjoint survey experiments_. Political Behavior, 40, 571–591.

## Citation 
If you use ```ConjointSensitivity``` in your research, please cite our paper:

Abramson, S., & Zafer, B. (2026) _Do Voters Prefer Women and Young Candidates? Re-evaluating Evidence from Conjoint Experiments_

## Installation

You can install the development version of ConjointSensitivity like so:

``` r
# install.packages("devtools")
devtools::install_github("zfrb/ConjointSensitivity")

```

## Quickstart

This example demonstrates how to use ConjointSensitivity using the replication data for the non-partisan YouGov experiment in Kirkland and Coppock (2018).

```{r example}
library(ConjointSensitivity)
library(dplyr, verbose = F, quietly = T)
library(torch)
library(purrr)

# Load the conjoint dataset
df <- read.csv("tests/testthat/testdata_KirklandCoppock_nonpartisan_yougov.csv")

```

### 1. Respondent Sensitivity 

```{r}
# Fit the base linear model
fit.lm <- lm(
  as.formula(win ~ cand_female + Age + Race + Job + Political), 
  data = df, 
  weights = weight, 
  x = TRUE, 
  y = TRUE
)

# Run the respondent-level analysis
respondent_results <- AnalyzeRespondentSensitivity(
  fit.lm = fit.lm, 
  segroup = df$caseid, 
  var_interest = "cand_female", 
  target = "sign", 
  dropped_resp_list = TRUE
)

# View main results 
respondent_results$RespondentSensitivity

# View dropped respondents  
respondent_results$DroppedRespondents
```

#### Visualising the Respondent Influences CDF
```{r plot}
plot_cdf_respondent_influences(fit.lm = fit.lm, segroup = df$caseid, var_interest = "cand_female", ndrop = 14)
```

### 2.Contest Sensitivity 


```{r}
contest_results <- AnalyzeContestSensitivity(
  formula = as.formula(win ~ cand_female + Age + Race + Job + Political), 
  data = as.data.frame(df), 
  respondent_id = "caseid", 
  contest_no = "contest_no", 
  var_interest = "cand_female", 
  target = "sign", 
  weights = "weight"
)

# View main results
contest_results$ContestSensitivity

# View dropped contests 
contest_results$DroppedContests

# View the mapping from profile attributes to contest ids.
head(contest_results$ProfileKey)
```


