---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ConjointSensitivity

<!-- badges: start -->
<!-- badges: end -->

This package is developed to ...

## Installation

You can install the development version of ConjointSensitivity like so:

``` r
# install.packages("devtools")
devtools::install_github("zfrb/ConjointSensitivity")

```

## Quickstart

This example demonstrates how to use ConjointSensitivity using the replication data for the non-partisan YouGov experiment in Kirkland and Coppock (2018).

```{r example}
library(ConjointSensitivity)
library(dplyr, quietly = T)
library(torch)
library(purrr)

# Load the conjoint dataset
df <- read.csv("tests/testthat/testdata_KirklandCoppock_nonpartisan_yougov.csv")

```

### 1. Respondent Sensitivity 

```{r}
# Fit the base linear model
fit.lm <- lm(
  as.formula(win ~ cand_female + Age + Race + Job + Political), 
  data = df, 
  weights = weight, 
  x = TRUE, 
  y = TRUE
)

# Run the respondent-level analysis
respondent_results <- AnalyzeRespondentSensitivity(
  fit.lm = fit.lm, 
  segroup = df$caseid, 
  var_interest = "cand_female", 
  target = "sign", 
  dropped_resp_list = TRUE
)

# View main results 
respondent_results$RespondentSensitivity

# View dropped respondents  
respondent_results$DroppedRespondents
```

#### Visualising the Respondent Influences CDF
```{r plot}
plot_cdf_respondent_influences(
  fit.lm = fit.lm,
  segroup = df$caseid,
  var_interest = "cand_female",
  ndrop = 14
)
```

### 2.Contest Sensitivity 


```{r}
contest_results <- AnalyzeContestSensitivity(
  formula = as.formula(win ~ cand_female + Age + Race + Job + Political), 
  data = as.data.frame(df), 
  respondent_id = "caseid", 
  contest_no = "contest_no", 
  var_interest = "cand_female", 
  target = "sign", 
  weights = "weight"
)

# View main results
contest_results$ContestSensitivity

# View dropped contests 
contest_results$DroppedContests

# View the mapping from profile attributes to contest ids.
head(contest_results$ProfileKey)
```


